---
title: "Goal1_Linear regression"
author: "Yunhui Qi"
date: "2019/4/3"
output: html_document
---

 This file is the second part of Goal 1.
 
 This should be run after Goal1_Get business scores.ipynb. 
 
 This file is to get coefficients of seven meaningful topics and 
 give quantative suggestions on how to improve ratings wrt review. 

 Note: please notice that we did not write details of this part in our summary, this is because we are not looking for a best model, we just want to provide some quantative description on our analysis before. We explain the results of linear regression in this file.

### Regression

```{r}
business_scores=read.csv("../data/business_scores.csv")
predictors = business_scores[,2:8]
weighted_star = business_scores$weighted_stars
summary(lm(weighted_star~.,data = predictors))
```

From the results above, we have several conclusion:

1. Coefficients: 

  When all other topic scores are fixed, weighted ratings will increase 0.8225 if score of Facilities increases by 1. 
  
  When all other topic scores are fixed, weighted ratings will increase 1.0843 if score of Courses increases by 1. 
  
  When all other topic scores are fixed, weighted ratings will increase 0.7164 if score of Service_and_Accessories increases by 1. 
  
  When all other topic scores are fixed, weighted ratings will increase 1.1960 if score of Membership_and_Price increases by 1. 
  
  When all other topic scores are fixed, weighted ratings will increase 0.6984 if score of Trainer increases by 1. 
  
  When all other topic scores are fixed, weighted ratings will increase 0.8813 if score of Time increases by 1.
  
  When all other topic scores are fixed, weighted ratings will increase 0.6448 if score of Environment increases by 1.
  
2. Confidence interval for coefficients:

We are 95% confident that our intervals contain the corresponding true coefficients' values.

3. Hypothesis testing for t tests:

For each coefficient $ \beta_{i} $, we have t test: $H_0: \beta_1 = 0$ vs $H_1: \beta_1 \neq 0$. The associated p-value for coefficients ar all less than 0.05.  We can declare that there is a linear relationship between topic score and weighted ratings. However, our conclusion carries a 5% error rate where we may have falsely declared that there is a relationship even though there truly isn't a relationship.

4. Hypothesis testing for F test: 

Using p value from F test which is less than 2.2*10^-16, we can conclude that our model is effective with 5% error rate.

5. $ R^2 $:

Abdomen and weight only explain about 12.96% of the variation in body fat %. Besides, compared with the full model which has adjusted $ R^2 $ equal to 12.63%, our model may not be appropriate

### Diagnostic

```{r}
layout(matrix(c(1,2,3,4),nrow=2))
plot(lm(weighted_star~.,data = predictors))
```


There are several important assumptions about linear regression. From diagnostic plots, we conclude:

1. Linearity: 

from the plot of fitted values versus residuals,linearity assumption may be violated.

2. Additivity:

seems reasonable from the interpretation of coefficients

3. Normally distributed errors: 

seems not that reasonable from the QQ plot.

4. Constant variance: 

the error terms do not have equal variance.

5. Outliers: 

from cook's distance, we do not have outliers.
